{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-03-28 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes, a lot

            % NECOARA ASSUMPTIONS 

@@

            % BREGMAN DIV DEFINITION

@@

            % STRONG CONVEXITY DEFINITION

@@

            % DEFINITION OF WEAKER STRONG CONVEXITY

@@

                    \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb G(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-eb} Error Bound (EB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. Denoted by $\mathbb E(L_f, \kappa_f, X)$. 

@@

@@

@@

@@

            The following theorems are about the relation between EB and QFG.

>>>>

            % NECOARA's ASSUMPTIONS ====================================================================================

@@

            % BREGMAN DIV DEFINITION ===================================================================================

@@

            % STRONG CONVEXITY DEFINITION ==============================================================================

@@

            % DEFINITION OF WEAKER STRONG CONVEXITY ====================================================================

@@

                    \item\label{def:neocara-qscnvx} Quasi-strong convexity (Q-SCNVX): $0 \le D_f(\bar x, x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
                    Denoeted by $\mathbb S'(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-qup} Quadratic under approximation (QUA): $0 \le D_f(x, \bar x) - \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
                    Denoeted by $\mathbb U(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-qgg} Quadratic Gradient Growth (QGG): $0\le D_f(x, \bar x) + D_f(\bar x, x) - \kappa_f/2\Vert x - \bar x\Vert^2$. 
                    Denoted by $\mathbb G(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-qfg} Quadratic Function Growth (QFG): $0 \le f(x) - f^* - \kappa_f/2\Vert x - \bar x\Vert^2$. 
                    Denoted by $\mathbb F(L_f, \kappa_f, X)$. 
                    \item\label{def:necoara-peb} Proximal Error Bound (PEB): $\Vert \mathcal G_{L_f}x\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
                    Denoted by $\mathbb E(L_f, \kappa_f, X)$. 

@@

            % THEOREM | Q-SCNVX IMPLIES QUA ============================================================================

@@

            % THEOREM | QGG IMPLIES QUA ================================================================================
            \begin{theorem}[QGG implies QUA]
                Let $f$ satisfies Assumption \ref{ass:necoara-2019-settings}, under convexity it has 
                    \mathbb G(L_f, \kappa_f, X)\subseteq \mathbb U(L_f, \kappa_f, X). 
                For all $x \in X$, define $\bar x = \Pi_{X^+}x$, $x_\tau = \bar x + \tau(x - \bar x)\; \forall \tau \in [0, 1]$. 
                Observe that $\frac{d}{d\tau}x_\tau = x - \bar x$ and $\Pi_{X^+}x_\tau = \bar x\; \forall \tau \in [0, 1]$. 
                Using calculus and Theorem \ref{def:necoara-weaker-scnvx} \ref{def:necoara-qgg}: 
                    f(x) &= f(\bar x) + \int_0^1 \langle \nabla f(x_\tau), x - \bar x\rangle d\tau  
                    &= f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
                    \int_0^1 \langle \nabla f(x_\tau) - \nabla f(\bar x), x - \bar x\rangle d \tau
                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
                    \int_0^1 \tau^{-1}\langle \nabla f(x_\tau) - \nabla f(\bar x), \tau(x - \bar x)\rangle d \tau
                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
                    \int_0^1 \tau^{-1}\langle \nabla f(x_\tau) - \nabla f(\bar x), x_\tau - \bar x\rangle d \tau
                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
                    \int_0^1 \tau^{-1}\kappa_f\Vert \tau(x - \bar x)\Vert^2 d \tau
                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
                    \int_0^1 \tau\kappa_f\Vert x - \bar x \Vert^2 d \tau
                    f(\bar x) + \langle \nabla f(\bar x), x - \bar x\rangle + 
                    \frac{\kappa}{2}\Vert x - \bar x\Vert^2. 
                This is Theorem 3 in Neocara et al. \cite{necoara_linear_2019}. 
                There is no immediaet use of convexity besides that the projection $\bar x = \Pi_{X^+}x$ is a singleton.
            % THEOREM | QFC IMPLIES QGG  ===============================================================================

@@

            % THEOREM | SUFFICIENCY OF QFG =============================================================================

@@

            The following theorems are about the relation between PEB and QFG. 
            \begin{theorem}{equivalence between QFG and PEB}
